Understanding Structure and Selectivity in Nanostructured Lyotropic Liquid Crystal Membranes using Molecular Simulations

### 2020-04-27 Ben_Manuscripts/thesis/stochastic_transport_si.tex
spell checking and mod to usage of subdiffusion

\documentclass{article}

% Table of contents formatting
\usepackage{tocloft}

\renewcommand\cftsecfont{\normalfont}
\renewcommand\cftsecpagefont{\normalfont}
\renewcommand{\cftsecleader}{\cftdotfill{\cftsecdotsep}}
\renewcommand\cftsecdotsep{\cftdot}
\renewcommand\cftsubsecdotsep{\cftdot}
\cftsetindents{section}{0em}{3em}
%\cftsetindents{subsection}{1em}{3em}

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{array}
\usepackage{multirow}

\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}

\externaldocument[M-]{ms}

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thepage}{S\arabic{page}}
\renewcommand{\thetable}{S\arabic{table}}

\title{Supporting Information: Capturing Subdiffusive Solute Dynamics and 
Predicting Selectivity in Nanoscale Pores with Time Series Modeling.}
\author{Benjamin J. Coscia \and Michael R. Shirts}

\begin{document}

  \maketitle
  %MRS10: be consistent on capitalization of section titles (And therefore table of contents)
  \tableofcontents
 \graphicspath{{./supporting_figures/}}
  \bibliographystyle{ieeetr}

@@

  \section{Solute Equilibration}\label{section:equilibration}

@@

  We chose to estimate the Hurst parameter, $H$ by a least squares fit to the analytical
  autocorrelation function for fractional Brownian motion (the variance-normalized version 
  of Equation~\ref{M-eqn:fbm_autocorrelation} in the main text):

  \begin{equation}
    \gamma(k) = \dfrac{1}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
  \label{eqn:fbm_autocorrelation}
  \end{equation}

  In Figure~\ref{fig:hurst_autocorrelation}, we plotted Equation~\ref{eqn:fbm_autocorrelation}
  for different values of $H$. When $H > 0.5$, Equation~\ref{eqn:fbm_autocorrelation} decays
  slowly to zero meaning one needs to study large time lags with high frequency in order to
  accurately estimate $H$ from the data. Fortunately, all of our solutes show anti-correlated
  motion, so most of the information in Equation \ref{eqn:fbm_autocorrelation} is contained
  within the first few lags.

@@

  The autocovariance function of fractional L\'evy motion is different from fractional
  Brownian motion (see Equations~\ref{M-eqn:fbm_autocorrelation}
  and~\ref{M-eqn:flm_autocovariance} of the main text), but their autocorrelation 
  structures are the same. The autocovariance function of FLM is dependent on the 
  expected value of squared draws from the underlying L\'evy distribution, $E\big[L(1)^2\big]$. 
  This is effectively the distribution's variance, which is undefined for most 
  L\'evy stable distributions due to their heavy tails. As a consequence, one should 
  expect $E\big[L(1)^2\big]$ to grow as more samples are drawn from the distribution
  with the autocovariance function responding accordingly. 
  However, we are only interested in the autocorrelation function. In order to predict
  the Hurst parameter from the autocorrelation function, we must show that it has 
  a well-defined structure and is independent of the coefficient in 
  Equation~\ref{M-eqn:flm_autocovariance} of the main text. In Figure~\ref{fig:flm_autocorrelation}, 
  we plot the average autocorrelation function from an FLM process with an increasing 
  number of observations per generated sequence. For all simulations we set $H$=0.35 
  and $\alpha$=1.4. The variance-normalized autocovariance function, i.e. the autocorrelation
  function, does not change with increasing sequence length. Additionally, the
  autocorrelation function of FBM, with the same $H$, is the same. Therefore we are 
  confident that we can use the same Hurst parameter as an input to both FBM and FLM
  simulations.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{URE_transitions.pdf}
  \caption{Urea}\label{fig:URE_transitions}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{GCL_transitions.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_transitions}
  \end{subfigure}
  \caption{As the timestep between observations increases, the probability
  transition matrix does not change significantly.}\label{fig:transitions}
  \end{figure}

@@

  To derive an analytical equation for the mean first passage time 
  (Equation~\ref{M-eqn:passage_times} of the main text), first consider an 
  initial pulse spreading out over time with a fixed mean. We can solve for the 
  time-dependent probability density of particle positions, $p$, by solving the one
  dimensional diffusion equation:
  \begin{equation}
  \frac{\partial p}{\partial t} = D \frac{\partial^2 p}{\partial z^2}
  \end{equation}
  The appropriate initial and boundary conditions are:
  $$BC1: t > 0, z = \infty, p = 0$$
  $$BC2: t > 0, z = 0, \frac{\partial p}{\partial z} = 0$$
  $$IC: t = 0, c = \delta(z)$$ % M\delta(z)
  %where $M$ is the total number of particles in the system. 
  It has been shown 
  elsewhere that the solution to this equation is:~\cite{cussler_diffusion:_2009}
  \begin{equation}
  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-z^2}{4Dt}\bigg)
  \end{equation}
  We can make the substitution $z = z - vt$, where $v$ represents a constant average
  velocity, in order to linearly shift the mean as a function of time:
  \begin{equation}
  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-(z - vt)^2}{4Dt}\bigg)
  \end{equation}
  One can track the fraction of particles, $F$, that have crossed the pore 
  boundary by integrating:
  \begin{equation}
  F(t) = \int_L^\infty p~dz = \mathrm{erfc}\bigg(\frac{L - vt}{2\sqrt{D t}}\bigg)
  \end{equation}
  where $L$ is the pore length. This represents the cumulative first passage 
  time distribution so we take its derivative in order to arrive at the first
  passage time distribution:
  \begin{equation}
  P(t) = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
  \label{eqn:passage_times}
  \end{equation} 
  where the only free parameters for fitting are $v$ and $D$. We calculated the
  expected value of Equation~\ref{eqn:passage_times} in order to get the MFPT. Specifically,
  we used the python package \texttt{scipy.integrate.quad} to numerically integrate:
  \begin{equation}
  E[t] = \int_0^\infty tP(t) dt
  \end{equation}

@@

  Analogous to Figure~\ref{M-fig:anticorrelated_hops} of the main text,
  Figure~\ref{fig:anticorrelated_hops} demonstrates that all solutes exhibit the
  same kind of anti-correlated hopping and trapping behavior.

  \begin{figure}[h]
  \centering
  % /figures/distributions_sfbm.py
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_GCL.pdf}
  \caption{}\label{fig:GCL_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{GCL_powerlaw.pdf}
  \caption{}\label{fig:GCL_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{GCL_hop_acf.pdf}
  \caption{}\label{fig:GCL_hop_acf}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_ACH.pdf}
  \caption{}\label{fig:ACH_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{ACH_powerlaw.pdf}
  \caption{}\label{fig:ACH_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{ACH_hop_acf.pdf}
  \caption{}\label{fig:ACH_hop_acf}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_MET.pdf}
  \caption{}\label{fig:MET_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{MET_powerlaw.pdf}
  \caption{}\label{fig:MET_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{MET_hop_acf.pdf}
  \caption{}\label{fig:MET_hop_acf}
  \end{subfigure}
  \caption{Hop length distributions, dwell time distributions and hop autocorrelation functions
  respectively for ethylene glycol (a-c), acetic acid (d-f) and methanol (g-i).
  See Section~\ref{M-section:AD_parameterization} of the main text for a more detailed discussion.
  }\label{fig:anticorrelated_hops}
  \end{figure}

@@

  When we use a pure power law distribution to parameterize the dwell time 
  distributions of the one and two mode AD models, the MD MSDs are severely 
  under-predicted because we are incorporating dwell times on the order of 
  the simulation length into simulated trajectories 
  (see Figure~\ref{fig:anomalous_msds_bothmode}). The parameters of the pure power law 
   distribution are included in Figure~\ref{fig:pure_power_law_params}.

  \begin{figure}[h]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{bothmode_msd_comparison_URE.pdf}
  \caption{Urea}\label{fig:bothmode_msd_comparison_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{bothmode_msd_comparison_GCL.pdf}
  \caption{Ethylene Glycol}\label{bothmode_msd_comparison_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{bothmode_msd_comparison_MET.pdf}
  \caption{Methanol}\label{fig:bothmode_msd_comparison_MET}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{bothmode_msd_comparison_ACH.pdf}
  \caption{Acetic Acid}\label{fig:bothmode_msd_comparison_ACH}
  \end{subfigure}
  \caption{When we do not apply an exponential cut-off to the power law
  distribution of dwell times,  MSDs are consistently under-predicted by the
  AD model.
  }\label{fig:anomalous_msds_bothmode}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_dwells.pdf}
  \caption{}\label{fig:1mode_AD_dwells}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_AD_dwells.pdf}
  \caption{}\label{fig:2mode_AD_dwells}
  \end{subfigure}
  \caption{We can parameterize the dwell time distribution in two ways: as a pure
  power law (P($\alpha$)) and as a power law with an exponential cut-off (P($\alpha$, $\lambda$)).
  Pure power laws have an infinite variance which allows extremely long dwell
  times to be sampled (see Figure~\ref{fig:anomalous_msds_bothmode}.
  }\label{fig:pure_power_law_params}
  \end{figure}

@@

  We evaluated the predictive capabilities of the AD modeling approach by training
  the model parameters on the first half of the equilibrated MD trajectory data and
  then comparing the MSD calculated from AD model realizations to the MSD calculated
  from the second half of the equilibrated MD trajectory data. This metric is
  only meaningful if the ensemble of solute trajectories is stationary. In 
  Figure~\ref{fig:msd_comparison}, we show that urea and acetic acid show acceptable
  stationary behavior while methanol and ethylene glycol do not.

@@

  \begin{figure}[h]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_MSD_halves.pdf}
  \caption{Urea}\label{fig:URE_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_MSD_halves.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_MSD_halves.pdf}
  \caption{Methanol}\label{fig:MET_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_MSD_halves.pdf}
  \caption{Acetic Acid}\label{fig:ACH_MSD_halves}
  \end{subfigure}
  \caption{The ensemble of solute trajectories may be stationary if the MSD
  calculated from different portions of the trajectory are the same. Here we
  plot the MSD calculated up to a 500 ns time lag of the first and second
  halves of the equilibrated solute trajectories. Urea and acetic acid have
  similar MSDs, providing evidence of stationarity, while the MSDs of 
  ethylene glycol and methanol are different suggesting that they are not.}\label{fig:msd_comparison}
  \end{figure}

@@

  %MRS8: how much of this is already in the main text?  Try to limit analysis that appears in the main text.
%  The under-estimate of urea's MSD at long timescales is due to long timescale
%  positional anti-correlation which may not be present in the molecularly 
%  detailed simulations of the system. The 
%  persistent curvature of the predicted MSD curves is a direct consequence of 
%  the Hurst parameter. Without anti-correlation, the process would be 
%  a pure CTRW for which one would expect the time averaged MSD curves to become 
%  linear.~\cite{meroz_toolbox_2015} It may be true that on the $\mu$s time scale, 
%  positional correlation is lost which would manifest as a transition from a sub-linear
%  to linear MSD curve. A solution for more accurately modeling this behavior in  
%  the future may be to truncate the positional autocorrelation function.~\cite{molina-garcia_crossover_2018}
%  
%  The under-estimate of the curvature of acetic acid's predicted MSD suggests that,
%  in this case, the AD model over-estimates the Hurst parameter. This is not surprising
%  because the Hurst parameter is challenging to quantify, especially with a relatively 
%  small amount of data (see Section~\ref{M-method:sfbm} of the main text for further discussion of this 
%  challenge). A more accurate measurement of $H$ would fix the shape of the MSD curve,
%  but also lower the predicted MSD meaning we are either underestimating the width of
%  the hop length distribution, favoring longer dwell times, or both.
%  
%  This brief qualitative analysis suggests two shortcomings of the AD model. First, in
%  a real system, positional anti-correlation may dissipate after a sufficiently long 
%  time lag, dependent on the solute being studied. Second, it is difficult to reliably
%  parameterize the Hurst parameter which is important for accurately describing the 
%  curvature of the solute MSDs.
%  
%  This analysis also suggests that working with only half of the data we collected
%  ($\sim$ 2 $\mu$s post-equilibration) is not always sufficient for extracting reliable
%  parameter estimates. In most cases, the magnitude of the MSD predictions after a 
%  500 ns time lag are within or close to within error of the MD MSDs (for sFBMcut and
%  sFLMcut), but still appear to systematically under-predict the mean. We may be
%  operating on the border of the minimum amount of data required to accurately 
%  parameterize the AD model. Longer simulations and more independent trajectories may
%  be necessary. Therefore, in the next section we will work with parameters fit to the
%  full equilibrated portion of the solute trajectories, doubling the data.

@@

  %MRS8: representations of the parameters, or representations of the graphs?  Or just tabulations of the data found in the graph.
  The tables in this section are tabular representations of the parameters depicted in
  Figures~\ref{M-fig:1mode_parameters} and~\ref{M-fig:2mode_parameters} of the main text
  and used to generate AD approach realizations whose MSDs are shown in Figure~\ref{M-fig:anomalous_msds}
  of the main text.

@@

  The following table is a tabular representation of the parameters 
  depicted in Figure~\ref{M-fig:msddm_parameters} of the main text.

>>>>

\chapter{Supporting Information to Chapter 4}\label{SI:ch4}

@@

  \section{Solute Equilibration}\label{S-section:equilibration4}

@@

  We chose to estimate the Hurst parameter, $H$ by a least squares fit to the analytical
  autocorrelation function for fractional Brownian motion (the variance-normalized version 
  of Equation~\ref{eqn:fbm_autocorrelation} in Chapter 4):

  \begin{equation}
    \gamma(k) = \dfrac{1}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
  \label{S-eqn:fbm_autocorrelation}
  \end{equation}

  In Figure~\ref{fig:hurst_autocorrelation}, we plotted Equation~\ref{S-eqn:fbm_autocorrelation}
  for different values of $H$. When $H > 0.5$, Equation~\ref{S-eqn:fbm_autocorrelation} decays
  slowly to zero meaning one needs to study large time lags with high frequency in order to
  accurately estimate $H$ from the data. Fortunately, all of our solutes show anti-correlated
  motion, so most of the information in Equation \ref{S-eqn:fbm_autocorrelation} is contained
  within the first few lags.

@@

  The autocovariance function of fractional L\'evy motion is different from fractional
  Brownian motion (see Equations~\ref{eqn:fbm_autocorrelation}
  and~\ref{eqn:flm_autocovariance} of the main text), but their autocorrelation 
  structures are the same. The autocovariance function of FLM is dependent on the 
  expected value of squared draws from the underlying L\'evy distribution, $E\big[L(1)^2\big]$. 
  This is effectively the distribution's variance, which is undefined for most 
  L\'evy stable distributions due to their heavy tails. As a consequence, one should 
  expect $E\big[L(1)^2\big]$ to grow as more samples are drawn from the distribution
  with the autocovariance function responding accordingly. 
  However, we are only interested in the autocorrelation function. In order to predict
  the Hurst parameter from the autocorrelation function, we must show that it has 
  a well-defined structure and is independent of the coefficient in 
  Equation~\ref{eqn:flm_autocovariance} of the main text. In Figure~\ref{fig:flm_autocorrelation}, 
  we plot the average autocorrelation function from an FLM process with an increasing 
  number of observations per generated sequence. For all simulations we set $H$=0.35 
  and $\alpha$=1.4. The variance-normalized autocovariance function, i.e. the autocorrelation
  function, does not change with increasing sequence length. Additionally, the
  autocorrelation function of FBM, with the same $H$, is the same. Therefore we are 
  confident that we can use the same Hurst parameter as an input to both FBM and FLM
  simulations.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{URE_transitions.pdf}
  \caption{Urea}\label{fig:URE_transitions}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{GCL_transitions.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_transitions}
  \end{subfigure}
  \caption{As the time step between observations increases, the probability
  transition matrix does not change significantly.}\label{fig:transitions}
  \end{figure}

@@

  To derive an analytical equation for the mean first passage time 
  (Equation~\ref{eqn:passage_times} of Chapter 4), first consider an 
  initial pulse spreading out over time with a fixed mean. We can solve for the 
  time-dependent probability density of particle positions, $p$, by solving the one
  dimensional diffusion equation:
  \begin{equation}
  \frac{\partial p}{\partial t} = D \frac{\partial^2 p}{\partial z^2}
  \end{equation}
  The appropriate initial and boundary conditions are:
  $$BC1: t > 0, z = \infty, p = 0$$
  $$BC2: t > 0, z = 0, \frac{\partial p}{\partial z} = 0$$
  $$IC: t = 0, c = \delta(z)$$ % M\delta(z)
  %where $M$ is the total number of particles in the system. 
  It has been shown 
  elsewhere that the solution to this equation is:~\cite{cussler_diffusion:_2009}
  \begin{equation}
  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-z^2}{4Dt}\bigg)
  \end{equation}
  We can make the substitution $z = z - vt$, where $v$ represents a constant average
  velocity, in order to linearly shift the mean as a function of time:
  \begin{equation}
  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}\exp\bigg(\frac{-(z - vt)^2}{4Dt}\bigg)
  \end{equation}
  One can track the fraction of particles, $F$, that have crossed the pore 
  boundary by integrating:
  \begin{equation}
  F(t) = \int_L^\infty p~dz = \mathrm{erfc}\bigg(\frac{L - vt}{2\sqrt{D t}}\bigg)
  \end{equation}
  where $L$ is the pore length. This represents the cumulative first passage 
  time distribution so we take its derivative in order to arrive at the first
  passage time distribution:
  \begin{equation}
  P(t) = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
  \label{S-eqn:passage_times}
  \end{equation} 
  where the only free parameters for fitting are $v$ and $D$. We calculated the
  expected value of Equation~\ref{S-eqn:passage_times} in order to get the MFPT. Specifically,
  we used the python package \texttt{scipy.integrate.quad} to numerically integrate:
  \begin{equation}
  E[t] = \int_0^\infty tP(t) dt
  \end{equation}

@@

  Analogous to Figure~\ref{fig:anticorrelated_hops},
  Figure~\ref{S-fig:anticorrelated_hops} demonstrates that all solutes exhibit the
  same kind of anti-correlated hopping and trapping behavior.

  \begin{figure}[h]
  \centering
  % /figures/distributions_sfbm.py
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_GCL.pdf}
  \caption{}\label{fig:GCL_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{GCL_powerlaw.pdf}
  \caption{}\label{fig:GCL_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{GCL_hop_acf.pdf}
  \caption{}\label{fig:GCL_hop_acf}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_ACH.pdf}
  \caption{}\label{fig:ACH_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{ACH_powerlaw.pdf}
  \caption{}\label{fig:ACH_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{ACH_hop_acf.pdf}
  \caption{}\label{fig:ACH_hop_acf}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_MET.pdf}
  \caption{}\label{fig:MET_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{MET_powerlaw.pdf}
  \caption{}\label{fig:MET_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{MET_hop_acf.pdf}
  \caption{}\label{fig:MET_hop_acf}
  \end{subfigure}
  \caption{Hop length distributions, dwell time distributions and hop autocorrelation functions
  respectively for ethylene glycol (a-c), acetic acid (d-f) and methanol (g-i).
  See Section~\ref{section:AD_parameterization} of the main text for a more detailed discussion.
  }\label{S-fig:anticorrelated_hops}
  \end{figure}

@@

  When we use a pure power law distribution to parameterize the dwell time 
  distributions of the one and two mode AD models, the MD MSDs are severely 
  under-predicted because we are incorporating dwell times on the order of 
  the simulation length into simulated trajectories 
  (see Figure~\ref{S-fig:anomalous_msds_bothmode}). The parameters of the pure power law 
   distribution are included in Figure~\ref{fig:pure_power_law_params}.

  \begin{figure}[h]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{bothmode_msd_comparison_URE.pdf}
  \caption{Urea}\label{S-fig:bothmode_msd_comparison_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{bothmode_msd_comparison_GCL.pdf}
  \caption{Ethylene Glycol}\label{S-bothmode_msd_comparison_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{bothmode_msd_comparison_MET.pdf}
  \caption{Methanol}\label{S-fig:bothmode_msd_comparison_MET}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{bothmode_msd_comparison_ACH.pdf}
  \caption{Acetic Acid}\label{S-fig:bothmode_msd_comparison_ACH}
  \end{subfigure}
  \caption{When we do not apply an exponential cut-off to the power law
  distribution of dwell times,  MSDs are consistently under-predicted by the
  AD model.
  }\label{S-fig:anomalous_msds_bothmode}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_AD_dwells.pdf}
  \caption{}\label{S-fig:1mode_AD_dwells}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_AD_dwells.pdf}
  \caption{}\label{S-fig:2mode_AD_dwells}
  \end{subfigure}
  \caption{We can parameterize the dwell time distribution in two ways: as a pure
  power law (P($\alpha$)) and as a power law with an exponential cut-off (P($\alpha$, $\lambda$)).
  Pure power laws have an infinite variance which allows extremely long dwell
  times to be sampled (see Figure~\ref{S-fig:anomalous_msds_bothmode}).
  }\label{fig:pure_power_law_params}
  \end{figure}

@@

  We evaluated the predictive capabilities of the AD modeling approach by training
  the model parameters on the first half of the equilibrated MD trajectory data and
  then comparing the MSD calculated from AD model realizations to the MSD calculated
  from the second half of the equilibrated MD trajectory data. This metric is
  only meaningful if the ensemble of solute trajectories is stationary. In 
  Figure~\ref{S-fig:msd_comparison}, we show that urea and acetic acid show acceptable
  stationary behavior while methanol and ethylene glycol do not.

@@

  \begin{figure}[h]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_MSD_halves.pdf}
  \caption{Urea}\label{fig:URE_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_MSD_halves.pdf}
  \caption{Ethylene Glycol}\label{fig:GCL_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_MSD_halves.pdf}
  \caption{Methanol}\label{fig:MET_MSD_halves}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_MSD_halves.pdf}
  \caption{Acetic Acid}\label{fig:ACH_MSD_halves}
  \end{subfigure}
  \caption{The ensemble of solute trajectories may be stationary if the MSD
  calculated from different portions of the trajectory are the same. Here we
  plot the MSD calculated up to a 500 ns time lag of the first and second
  halves of the equilibrated solute trajectories. Urea and acetic acid have
  similar MSDs, providing evidence of stationarity, while the MSDs of 
  ethylene glycol and methanol are different suggesting that they are not.}\label{S-fig:msd_comparison}
  \end{figure}

@@

  %MRS8: how much of this is already in the main text?  Try to limit analysis that appears in the main text.
%  The under-estimate of urea's MSD at long timescales is due to long timescale
%  positional anti-correlation which may not be present in the molecularly 
%  detailed simulations of the system. The 
%  persistent curvature of the predicted MSD curves is a direct consequence of 
%  the Hurst parameter. Without anti-correlation, the process would be 
%  a pure CTRW for which one would expect the time averaged MSD curves to become 
%  linear.~\cite{meroz_toolbox_2015} It may be true that on the $\mu$s time scale, 
%  positional correlation is lost which would manifest as a transition from a sub-linear
%  to linear MSD curve. A solution for more accurately modeling this behavior in  
%  the future may be to truncate the positional autocorrelation function.~\cite{molina-garcia_crossover_2018}
%  
%  The under-estimate of the curvature of acetic acid's predicted MSD suggests that,
%  in this case, the AD model over-estimates the Hurst parameter. This is not surprising
%  because the Hurst parameter is challenging to quantify, especially with a relatively 
%  small amount of data (see Section~\ref{method:sfbm} of the main text for further discussion of this 
%  challenge). A more accurate measurement of $H$ would fix the shape of the MSD curve,
%  but also lower the predicted MSD meaning we are either underestimating the width of
%  the hop length distribution, favoring longer dwell times, or both.
%  
%  This brief qualitative analysis suggests two shortcomings of the AD model. First, in
%  a real system, positional anti-correlation may dissipate after a sufficiently long 
%  time lag, dependent on the solute being studied. Second, it is difficult to reliably
%  parameterize the Hurst parameter which is important for accurately describing the 
%  curvature of the solute MSDs.
%  
%  This analysis also suggests that working with only half of the data we collected
%  ($\sim$ 2 $\mu$s post-equilibration) is not always sufficient for extracting reliable
%  parameter estimates. In most cases, the magnitude of the MSD predictions after a 
%  500 ns time lag are within or close to within error of the MD MSDs (for sFBMcut and
%  sFLMcut), but still appear to systematically under-predict the mean. We may be
%  operating on the border of the minimum amount of data required to accurately 
%  parameterize the AD model. Longer simulations and more independent trajectories may
%  be necessary. Therefore, in the next section we will work with parameters fit to the
%  full equilibrated portion of the solute trajectories, doubling the data.

@@

  %MRS8: representations of the parameters, or representations of the graphs?  Or just tabulations of the data found in the graph.
  The tables in this section are tabular representations of the parameters depicted in
  Figures~\ref{fig:1mode_parameters} and~\ref{fig:2mode_parameters} of the main text
  and used to generate AD approach realizations whose MSDs are shown in Figure~\ref{fig:anomalous_msds}
  of the main text.

@@

  The following table is a tabular representation of the parameters 
  depicted in Figure~\ref{fig:msddm_parameters} of the main text.

  \begin{table}[h]
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
  \hline
  & \multicolumn{3}{c|}{Urea} & \multicolumn{3}{c|}{Ethylene Glycol} & \multicolumn{3}{c|}{Methanol} & \multicolumn{3}{c|}{Acetic Acid} \\\hline
  State & H     &$\alpha_h$& $\sigma$ & H    &$\alpha_h$& $\sigma$   & H     &$\alpha_h$& $\sigma$ & H    &$\alpha_h$& $\sigma$ \\\hline
  1     & 0.10  & 1.79     & 0.034    & 0.09 & 1.68     & 0.045      & 0.11  & 1.56     & 0.052    & 0.10 & 1.78     & 0.035    \\
  2     & 0.06  & 1.80     & 0.033    & 0.09 & 1.75     & 0.037      & 0.07  & 1.63     & 0.043    & 0.08 & 1.88     & 0.032    \\
  3     & 0.11  & 1.88     & 0.030    & 0.11 & 1.86     & 0.030      & 0.02  & 1.80     & 0.036    & 0.04 & 2.00     & 0.030    \\
  4     & 0.10  & 1.95     & 0.027    & 0.04 & 1.91     & 0.028      & 0.02  & 1.75     & 0.036    & 0.04 & 2.00     & 0.027    \\
  5     & 0.19  & 1.34     & 0.048    & 0.15 & 1.40     & 0.062      & 0.10  & 1.28     & 0.074    & 0.13 & 1.47     & 0.048    \\
  6     & 0.15  & 1.45     & 0.040    & 0.11 & 1.52     & 0.040      & 0.03  & 1.50     & 0.042    & 0.09 & 1.70     & 0.038    \\
  7     & 0.15  & 1.61     & 0.032    & 0.05 & 1.60     & 0.040      & 0.28  & 1.20     & 0.043    & 0.08 & 1.77     & 0.031    \\
  8     & 0.11  & 1.71     & 0.028    & 0.05 & 1.74     & 0.030      & 0.04  & 1.83     & 0.037    & 0.01 & 2.00     & 0.030    \\
  T     & 0.34  & 1.42     & 0.036    & 0.37 & 1.44     & 0.045      & 0.35  & 1.45     & 0.057    & 0.34 & 1.54     & 0.040    \\\hline
  \end{tabular}
  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
  trajectories and used them to generate realizations of our MSDDM model. The states
  are defined in Table~\ref{table:states} of the main text except state T which 
  describes the transition emissions.}\label{table:msddm_params}
  \end{table}

% This is not used I think
%  \section{2-state MSDDM parameters}\label{section:simple_msddm_params}
%  
%  We used a simple 2-state model to illustrate how the self-transition probability 
%  effects simulated MSDs generated from the MSDDM. We used the following parameters:
%  
%  \begin{table}[h]
%  \centering
%  \begin{tabular}{|c|c|c|c|}
%  \hline
%  State & H     & $\alpha_h$ & $\sigma$ \\\hline
%  1     & 0.1  & 1.7       & 0.04    \\
%  2     & 0.2  & 1.5       & 0.04    \\
%  T     & 0.4  & 1.4       & 0.04    \\\hline
%  \end{tabular}
%  \caption{Values of $H$, $\alpha_h$ and $\sigma$ used to simulate realizations
%  of the simple MSDDM whose MSDs are shown in Figure~\ref{fig:T_sensitivity} of
%  the main text. The values are chosen to be similar to those in Table~\ref{table:msddm_params}
%  of the main text.}\label{table:msddm_params}
%  \end{table}
